Figure 3. Tissue Microbiome Abundances

### 2023-03-08 reports/manuscript/Figure3.Rmd
add figure legend

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  fig.align = "center",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  # remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results    = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width  = 6.6929133858,
  fig.align  = "center",
  fig.path   ="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r Load-data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(vegan)
  library(RColorBrewer)
  # remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

**Fig. 3 Identification of a distinct ectocervical tissue-adherent microbiome.** Ectocervical tissue samples were assessed for presence of a tissue-adherent microbiome. a Bar plots of alpha diversity indices and taxonomy profiles for each individual tissue sample. Color-coded squares above the stacked bar plots show bacterial vaginosis (BV, binned Nugent’s scores) and HIV diagnosis, respectively. Gray: negative, orange: intermediate, red: positive BV; Gray: HIV seronegative, red: HIV seropositive. b Total relative abundance in the luminal and tissue microbiome datasets. All taxa with a total relative abundance < 0.55 are included in the “other” category. c Microbiome profile shift between luminal and tissue
